The elusive benefits of vagueness

### 2018-04-22 papers/2018-v-book/review-dan-lassiter/vagueness-springer-review.tex
add Dan Lassiter review

p.18 \emph{allowed participants to use a comparison “algorithm” – the work of Justin Halberda and collaborators on the verification strategies associated with \emph{most} and \emph{more than half} is highly relevant here (and indeed throughout the paper, given that \emph{most} is vague but otherwise fairly similar in meaning to \emph{more than half})

@@

p.19 Testing (H1), we have \emph{Vague instructions were non-significantly easier \ldots} do you mean \emph{not significantly easier}? In any case from the graphs on the next page this seems misleading – what it looks like is a substantial main effect where vague instructions have a main effect of lowering the response time, but this effect is masked by interactions with quantity, most notably (again) the huge speed-up for 6 in the matching/crisp condition. I'd recommend following the method described in Roger Levy}s paper on finding main effects in the presence of interactions, available here: \url{https://arxiv.org/abs/1405.2094}.

>>>>

p.18 \emph{allowed participants to use a comparison "algorithm"} – the work of Justin Halberda and collaborators on the verification strategies associated with \emph{most} and \emph{more than half} is highly relevant here (and indeed throughout the paper, given that \emph{most} is vague but otherwise fairly similar in meaning to \emph{more than half})

@@

p.19 Testing (H1), we have \emph{Vague instructions were non-significantly easier \ldots} do you mean \emph{not significantly easier}? In any case from the graphs on the next page this seems misleading – what it looks like is a substantial main effect where vague instructions have a main effect of lowering the response time, but this effect is masked by interactions with quantity, most notably (again) the huge speed-up for 6 in the matching/crisp condition. I'd recommend following the method described in Roger Levy's paper on finding main effects in the presence of interactions, available here: \url{https://arxiv.org/abs/1405.2094}.
